---
title: "scrape_sdwis_r01"
author: "Jim Sheehan"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


https://heads0rtai1s.github.io/2019/10/03/reticulate-intro/


```{r message=FALSE}

library(readr)
library(xml2)
library(lubridate)
library(dplyr)
library(ggplot2)

```


#### too many viols, need to loop

+ loop by state, well under 100000 max
+ warning is for extra empty column, ignore

```{r warning=FALSE}

datetime <- gsub(" ", "_", Sys.time())
datetime <- gsub(":", "-", datetime)


url_epa01_wsys <-
  "https://data.epa.gov/efservice/WATER_SYSTEM/EPA_REGION/01/PWS_ACTIVITY_CODE/A/CSV"

water_system_fresh <- read_csv(url_epa01_wsys, col_types = cols(.default = "c"))


pac_vals <- sort(unique(water_system_fresh$WATER_SYSTEM.PRIMACY_AGENCY_CODE))

url_base_viol <- "https://data.epa.gov/efservice/VIOLATION/PWS_ACTIVITY_CODE/A/PRIMACY_AGENCY_CODE/"

violation_fresh <- list()

for (i in 1:length(pac_vals)) {
  viols <- read_csv(paste0(url_base_viol, pac_vals[i], "/CSV"),
                    col_types = cols(.default = "c"))
  violation_fresh[[i]] <- viols
  
}


violation_fresh <- do.call(bind_rows, violation_fresh)


violation_fresh %>% 
  group_by(VIOLATION.PRIMACY_AGENCY_CODE) %>% 
  tally()


violation_fresh %>%
  write_csv(paste0("C:/Users/Jim/OneDrive/CFB/R_exports/SDWIS_tracking/violation_",
                   datetime, ".csv"))
water_system_fresh %>%
  write_csv(paste0("C:/Users/Jim/OneDrive/CFB/R_exports/SDWIS_tracking/water_system_", datetime, ".csv"))


```




*try public notification tier*

*try scheduler addin*




```{r}

violation_fresh <- violation_fresh %>% 
  mutate(VIOLATION.COMPL_PER_BEGIN_DATE = dmy(VIOLATION.COMPL_PER_BEGIN_DATE)) %>% 
  filter(TRUE)

summary(violation_fresh$VIOLATION.COMPL_PER_BEGIN_DATE)

```




#### MISC


*What is easiest way to get violation for PWSID and model it?*



```{r}

violations <- violation_fresh %>% 
  rename_all(~sub(".*\\.", "", .))

water_systems <- water_system_fresh %>% 
  rename_all(~sub(".*\\.", "", .))



violhistory <- violations %>%
  mutate(CPBD_YEAR = year(COMPL_PER_BEGIN_DATE)) %>% 
  group_by(PWSID, CPBD_YEAR, IS_HEALTH_BASED_IND) %>% 
  tally() %>% 
  tidyr::pivot_wider(names_from = IS_HEALTH_BASED_IND,
                     names_prefix = "HB_",
                     values_from = n,
                     values_fill = list(n = 0))

head(violhistory)

```

#### more violation table features (one column to 0/1 in function or after)

```{r}

# violhistory <- 
NHB_VCC <- violations %>%
  mutate(CPBD_YEAR = year(COMPL_PER_BEGIN_DATE)) %>% 
  filter(IS_HEALTH_BASED_IND == "N") %>% 
  group_by(PWSID, CPBD_YEAR, VIOLATION_CATEGORY_CODE) %>% 
  tally() %>% 
  tidyr::pivot_wider(names_from = VIOLATION_CATEGORY_CODE,
                     names_prefix = "NHB_",
                     values_from = n,
                     values_fill = list(n = 0))

head(NHB_VCC)

```





```{r}

fulldata <- violhistory %>% 
  right_join(water_systems, ., by = "PWSID") %>% 
  select(PWSID, NPM_CANDIDATE, PRIMACY_AGENCY_CODE, 
                    PWS_TYPE_CODE, GW_SW_CODE, 
                    OWNER_TYPE_CODE:SERVICE_CONNECTIONS_COUNT, 
                    CPBD_YEAR:HB_Y) %>% 
  mutate_at(vars(HB_N, HB_Y), ~if_else(. > 0, 1, 0)) %>% 
  mutate(POPULATION_SERVED_COUNT = as.numeric(POPULATION_SERVED_COUNT))

head(fulldata)

```

## (potential) feature engineering

```{r}

feat1 <- fulldata %>% 
  group_by(PWS_TYPE_CODE, PWSID) %>% 
  summarise(min_CPBD_YEAR = min(CPBD_YEAR),
            max_CPBD_YEAR = max(CPBD_YEAR),
            dif_CPBD_YEAR = max_CPBD_YEAR - min_CPBD_YEAR,
            sum_HB_N = sum(HB_N),
            sum_HB_Y = sum(HB_Y)) 

feat1 %>% 
  ggplot(aes(x = dif_CPBD_YEAR, y = sum_HB_Y, color = PWS_TYPE_CODE)) +
  geom_jitter(shape = 1) +
  geom_smooth(method = "lm")


feat1 %>% 
  ggplot(aes(x = dif_CPBD_YEAR, fill = PWS_TYPE_CODE)) +
  geom_histogram(binwidth = 1)


```



```{r}

YearMod <- 2016

traintestdat <- list()

PWS_TYPE_CODES <- unique(fulldata$PWS_TYPE_CODE)

for(i in 1:length(PWS_TYPE_CODES)) {
  index <- fulldata %>% 
  filter(CPBD_YEAR == YearMod, 
         PWS_TYPE_CODE == PWS_TYPE_CODES[i]) %>% 
  .$PRIMACY_AGENCY_CODE %>% 
  caret::createDataPartition(., times = 1, p = 0.20, list = FALSE)
  test <- fulldata %>% 
    filter(CPBD_YEAR == YearMod, 
         PWS_TYPE_CODE == PWS_TYPE_CODES[i]) %>% 
    slice(index) %>% 
    mutate(set = "test")
  train <- fulldata %>% 
    filter(CPBD_YEAR == YearMod, 
         PWS_TYPE_CODE == PWS_TYPE_CODES[i]) %>% 
    slice(-index) %>% 
    mutate(set = "train")
  traintestdat[[i]] <- bind_rows(train, test)
}

traintestdat <- do.call(bind_rows, traintestdat)

traintestdat

```


#### adding in systems with a violation history as of the modelled year


```{r}

violations %>% 
  mutate(CPBD_YEAR = year(COMPL_PER_BEGIN_DATE)) %>% 
  filter(CPBD_YEAR <= YearMod) %>% 
  select(PWSID) %>% 
  distinct() %>% 
  filter(!PWSID %in% traintestdat$PWSID)
  


```






*if need be, can put 01 in train*

```{r}

traintestdat %>% 
  group_by(PWS_TYPE_CODE, set, PRIMACY_AGENCY_CODE) %>% 
  tally() %>% 
  tidyr::spread(set, n)

```


```{r}

round(prop.table(
  table(traintestdat[traintestdat$PWS_TYPE_CODE == "CWS", ]$PRIMACY_AGENCY_CODE,
        traintestdat[traintestdat$PWS_TYPE_CODE == "CWS", ]$set),
  margin = 2
), 3)

```


```{r}

feat1_toyear <- fulldata %>% 
  filter(CPBD_YEAR <= YearMod) %>% 
  group_by(PWS_TYPE_CODE, PWSID) %>% 
  summarise(min_CPBD_YEAR = min(CPBD_YEAR),
            max_CPBD_YEAR = max(CPBD_YEAR),
            dif_CPBD_YEAR = max_CPBD_YEAR - min_CPBD_YEAR,
            first_YEAR = as.numeric(dif_CPBD_YEAR == 0),
            sum_HB_N = sum(HB_N),
            sum_HB_Y = sum(HB_Y)) 

head(feat1_toyear)

```



```{r}

traintestdat <- feat1_toyear %>% ungroup() %>% 
  select(-PWS_TYPE_CODE) %>% 
  inner_join(traintestdat, ., by = "PWSID")

traintestdat

```











```{r}

predmodel <- traintestdat %>% 
  mutate(HB_Yf = factor(HB_Y)) %>% 
  filter(PWS_TYPE_CODE == "CWS", set == "train") %>% 
  glm(dif_CPBD_YEAR ~ HB_Yf, data = .)

summary(predmodel)

plot(allEffects(predmodel))

```



```{r}

predmodel <- traintestdat %>% 
  filter(PWS_TYPE_CODE == "CWS", set == "train") %>% 
  glm(dif_CPBD_YEAR ~ HB_Y, data = .)

pred <- traintestdat %>% 
  filter(PWS_TYPE_CODE == "CWS", set == "test") %>% 
  select(PWSID, HB_Y) %>% 
  predict(predmodel, newdata = ., type = "response", se.fit = TRUE) %>% 
  as.data.frame()


traintestdat %>% 
  filter(PWS_TYPE_CODE == "CWS", set == "test") %>% 
  bind_cols(., pred) %>% 
  ggplot(aes(x = factor(HB_Y), y = dif_CPBD_YEAR, group = HB_Y)) +
  geom_boxplot() +
  geom_errorbar(aes(x = factor(HB_Y), ymin = fit - se.fit, ymax = fit + se.fit), 
                color = "red") +
  geom_point(aes(x = factor(HB_Y), y = fit), color = "red")
  



```




#### Logistic regression with effects plot


```{r}
table(traintestdat$PWS_TYPE_CODE)

model1 <- glm(HB_Y ~
                log(POPULATION_SERVED_COUNT) + 
#                POPULATION_SERVED_COUNT +
#                sum_HB_N +
                dif_CPBD_YEAR +
                first_YEAR +
                PWS_TYPE_CODE +
                GW_SW_CODE,
              family = binomial(),
              data = traintestdat,
              subset = set == "train")

summary(model1)

car::vif(model1)

```


```{r}

lmtest::lrtest(model1, . ~ . - dif_CPBD_YEAR)

```



```{r}
model1 <- glm(HB_Y ~
                dif_CPBD_YEAR +
                first_YEAR +
                PWS_TYPE_CODE +
                GW_SW_CODE,
              family = binomial(),
              data = trainset)

jtools::summ(model1)
```






```{r}

library(effects)



```


```{r}

plot(predictorEffect("dif_CPBD_YEAR", model1))

pe1 <- predictorEffects(model1, ~dif_CPBD_YEAR + PWS_TYPE_CODE)

plot(pe1)

# plot(pe1[[1]], main = "dif_CPBD_YEAR effect")
# plot(pe1[[2]], main = "PWS_TYPE_CODE effect")

```


### Accuracy



```{r}

pred_model1 <- predict(model1, 
                       newdata = traintestdat[traintestdat$set == "test",], 
                       type = "response")

summary(pred_model1)

```



```{r}

roc_df <- rbind(
  data.frame(
    predictor =
    predict(model1, 
            traintestdat[traintestdat$set == "train", ]),
    known.truth = traintestdat[traintestdat$set == "train", ]$HB_Y,
    model = "train"
  ),
  data.frame(
    predictor = predict(model1, 
            traintestdat[traintestdat$set == "test", ]),
    known.truth = traintestdat[traintestdat$set == "test", ]$HB_Y,
    model = "test"
  )
)



ggplot(roc_df, aes(d = known.truth, m = predictor, color = model)) + 
  plotROC::geom_roc(n.cuts = 0)



```




**Just a test of partitioning, better to bootstrap diff in means by year using all data I believe**


```{r}

YearModBoot <- 2015


bootdat <- fulldata %>% 
  filter(CPBD_YEAR <= YearModBoot) %>% 
  group_by(PWSID) %>% 
  summarise(min_CPBD_YEAR = min(CPBD_YEAR),
            max_CPBD_YEAR = max(CPBD_YEAR),
            dif_CPBD_YEAR = max_CPBD_YEAR - min_CPBD_YEAR,
            sum_HB_N = sum(HB_N),
            sum_HB_Y = sum(HB_Y)) %>% 
  filter(max_CPBD_YEAR == YearModBoot) %>% 
  inner_join(., fulldata[fulldata$CPBD_YEAR == YearModBoot, ], by = "PWSID") %>% 
  select(dif_CPBD_YEAR, HB_Y) %>% 
  mutate(HB_Y = factor(HB_Y)) %>% 
  as.data.frame()




```




```{r}

library(boot)


meanDiff =function(x, w){
    y <- tapply(x[w,1], x[w,2], mean)
    y[1]-y[2]}


totalBoot = boot(bootdat, meanDiff, R = 10000, strata = bootdat[,2])

# Takes a while, need high R = 10000
totalBootCI = boot.ci(totalBoot)

totalBoot

totalBootCI
```



```{r}

bootdat %>% 
  group_by(HB_Y) %>% 
  summarise(meandif_CPBD_YEAR = mean(dif_CPBD_YEAR)) %>% 
  tidyr::spread(HB_Y, meandif_CPBD_YEAR) %>% 
  mutate(meandif = `0` - `1`)

```




*** 

OLD

```{r}

url1 <- "https://data.epa.gov/efservice/WATER_SYSTEM/PRIMACY_AGENCY_CODE/MA/CITY_NAME/ANDOVER/ROWS/0:10/CSV"

url2 <- "https://data.epa.gov/efservice/WATER_SYSTEM/PRIMACY_AGENCY_CODE/MA/CSV"

url3 <- "https://data.epa.gov/efservice/WATER_SYSTEM/PRIMACY_AGENCY_CODE/MA/CITY_NAME/BRAINTREE/VIOLATION/CSV"

url4 <- "https://data.epa.gov/efservice/VIOLATION/PRIMACY_AGENCY_CODE/MA/CSV"


url5 <- "https://data.epa.gov/efservice/VIOLATION/PRIMACY_AGENCY_CODE/MA/PWSID/MA4239049"

url6 <- "https://data.epa.gov/efservice/VIOLATION/PRIMACY_AGENCY_CODE/MA/PWSID/MA4239049/CSV"

url7 <- "https://data.epa.gov/efservice/LCR_SAMPLE/PRIMACY_AGENCY_CODE/MA/CSV"


url8 <- "https://data.epa.gov/efservice/VIOLATION/EPA_REGION/01/CONTAMINANT_CODE/BEGINNING/28/CSV"


# BEGINNING
# can't do?:
# "COMPL_PER_BEGIN_DATE/>"

```





```{r}

tmp_xml <- xml2::read_xml(url5)

# xml_child(tmp_xml, 1)

```



```{r}
url4
violations_fresh <- read_csv(url4, col_types = cols(.default = "c")) %>% 
  mutate(VIOLATION.COMPL_PER_BEGIN_DATE = dmy(VIOLATION.COMPL_PER_BEGIN_DATE)) %>% 
  filter(TRUE)
names(violations_fresh)
```


```{r}

summary(violations_fresh$VIOLATION.COMPL_PER_BEGIN_DATE)


```






```{r}
url7
lcr_sample_fresh <- read_csv(url7, col_types = cols(.default = "c")) %>% 
  mutate(VIOLATION.COMPL_PER_BEGIN_DATE = dmy(VIOLATION.COMPL_PER_BEGIN_DATE))

```



```{r}
url8 <- "https://data.epa.gov/efservice/VIOLATION/EPA_REGION/01/CONTAMINANT_CODE/BEGINNING/40/CSV"
violations_fresh_cont <- read_csv(url8, col_types = cols(.default = "c"))

```

#### too many viols!!, need to loop

```{r}

datetime <- gsub(" ", "_", Sys.time())
datetime <- gsub(":", "-", datetime)

url_epa01_viol <- "https://data.epa.gov/efservice/VIOLATION/EPA_REGION/01/CSV"
url_epa01_wsys <- "https://data.epa.gov/efservice/WATER_SYSTEM/EPA_REGION/01/CSV"

violation_fresh <- read_csv(url_epa01_viol, col_types = cols(.default = "c"))
water_system_fresh <- read_csv(url_epa01_wsys, col_types = cols(.default = "c"))


violations_fresh %>% write_csv(paste0("export/r01/violation_", datetime, ".csv"))
water_system_fresh %>% write_csv(paste0("export/r01/water_system_", datetime, ".csv"))


```



*** 

#### Random sample method

**slow loop, try to speed up with apply (first)**

```{r}
set.seed(145)
index_ws <- sample(nrow(water_systems), size = 100)

system.time({
  ws_list <- list()
  for (i in 1:length(index_ws)) {
    vtable <- violations %>%
      filter(PWSID %in% water_systems[index_ws[i], ]$PWSID) %>%
      mutate(cpbd_year = year(COMPL_PER_BEGIN_DATE),
             IS_HEALTH_BASED_IND = IS_HEALTH_BASED_IND)
    
    vtable_hb <- vtable %>%
      group_by(PWSID, cpbd_year, IS_HEALTH_BASED_IND) %>%
      tally() %>%
      tidyr::pivot_wider(
        names_from = IS_HEALTH_BASED_IND,
        names_prefix = "HB_",
        values_from = n,
        values_fill = list(n = 0)
      )
    
    vtable_yhb_cont <- vtable %>%
      filter(IS_HEALTH_BASED_IND == "Y") %>%
      group_by(cpbd_year, IS_HEALTH_BASED_IND, CONTAMINANT_CODE) %>%
      tally()
    
    vtable_nhb_cont <- vtable %>%
      filter(IS_HEALTH_BASED_IND == "N") %>%
      group_by(cpbd_year, IS_HEALTH_BASED_IND, CONTAMINANT_CODE) %>%
      tally()
    
    # use nrow, no error if 0 rows
    set.seed(123) ####! just for speed comparison with loop, comment out final
    pick1 <- sample(nrow(vtable_hb), size = 1)
    
    hb_pick <- vtable_hb[pick1, ]
    
    hb_pick <- hb_pick %>%
      mutate(
        HB_Y_prioryear = if_else((cpbd_year - 1) %in% vtable_yhb_cont$cpbd_year, 1, 0),
        HB_N_prioryear = if_else((cpbd_year - 1) %in% vtable_nhb_cont$cpbd_year, 1, 0)
      )
    
    
    if (nrow(vtable) > 0) {
      hist <-
        cbind(
          minYear = min(vtable$cpbd_year),
          maxYear = max(vtable$cpbd_year)
        )
    } else{
      hist <- c(minYear = NA, maxYear = NA)
    }
    
    
    if (!is.na(hist[1])) {
      hb_pick <- hb_pick %>%
        mutate(ViolTableAge = cpbd_year - hist[1])
    } else{
      hb_pick <- hb_pick %>%
        mutate(ViolTableAge = NA)
    }
    
    # if no violation table data, make a table for PWSID with cpbd_year = code 9999
    if (nrow(hb_pick) == 0) {
      hb_pick <-
        tibble(PWSID = water_systems[index_ws[i], ]$PWSID, cpbd_year = 9999) %>% 
        group_by(PWSID)
    }
    
    ws_list[[i]] <-
      list(
        hb_pick = hb_pick,
        vtable_yhb_cont = vtable_yhb_cont,
        vtable_nhb_cont = vtable_nhb_cont,
        hist = hist
      )
  }
})



```



```{r}

SampleFun <- function(x){
      
    vtable <- violations %>%
      filter(PWSID %in% water_systems[index_ws[x], ]$PWSID) %>%
      mutate(cpbd_year = year(COMPL_PER_BEGIN_DATE),
             IS_HEALTH_BASED_IND = IS_HEALTH_BASED_IND)
    
    vtable_hb <- vtable %>%
      group_by(PWSID, cpbd_year, IS_HEALTH_BASED_IND) %>%
      tally() %>%
      tidyr::pivot_wider(
        names_from = IS_HEALTH_BASED_IND,
        names_prefix = "HB_",
        values_from = n,
        values_fill = list(n = 0)
      )
    
    vtable_yhb_cont <- vtable %>%
      filter(IS_HEALTH_BASED_IND == "Y") %>%
      group_by(cpbd_year, IS_HEALTH_BASED_IND, CONTAMINANT_CODE) %>%
      tally()
    
    vtable_nhb_cont <- vtable %>%
      filter(IS_HEALTH_BASED_IND == "N") %>%
      group_by(cpbd_year, IS_HEALTH_BASED_IND, CONTAMINANT_CODE) %>%
      tally()
    
    # use nrow, no error if 0 rows
    set.seed(123) ####! just for speed comparison with loop, comment out final
    pick1 <- sample(nrow(vtable_hb), size = 1)
    
    hb_pick <- vtable_hb[pick1, ]
    
    hb_pick <- hb_pick %>%
      mutate(
        HB_Y_prioryear = if_else((cpbd_year - 1) %in% vtable_yhb_cont$cpbd_year, 1, 0),
        HB_N_prioryear = if_else((cpbd_year - 1) %in% vtable_nhb_cont$cpbd_year, 1, 0)
      )
    
    
    if (nrow(vtable) > 0) {
      hist <-
        cbind(
          minYear = min(vtable$cpbd_year),
          maxYear = max(vtable$cpbd_year)
        )
    } else{
      hist <- c(minYear = NA, maxYear = NA)
    }
    
    
    if (!is.na(hist[1])) {
      hb_pick <- hb_pick %>%
        mutate(ViolTableAge = cpbd_year - hist[1])
    } else{
      hb_pick <- hb_pick %>%
        mutate(ViolTableAge = NA)
    }
    
    # if no violation table data, make a table for PWSID with cpbd_year = code 9999
    if (nrow(hb_pick) == 0) {
      hb_pick <-
        tibble(PWSID = water_systems[index_ws[x], ]$PWSID, cpbd_year = 9999) %>% 
        group_by(PWSID)
    }
    
    
    list(
        hb_pick = hb_pick,
        vtable_yhb_cont = vtable_yhb_cont,
        vtable_nhb_cont = vtable_nhb_cont,
        hist = hist
      )
    
  }



system.time({
  
  
 ws_list2 <- lapply(1:length(index_ws), SampleFun)
  
  
  
})

```



```{r}

lapply(1, SampleFun)


```


```{r}
water_systems[1, ]
```





```{r}
ws_list[[i]]

ws_list[[8]]

```


```{r}

hb_pick_df <- do.call(rbind, lapply(ws_list[1:length(ws_list)], '[[', 1))
head(hb_pick_df)

```





***

## MISC

#### Inactives

```{r warning=FALSE}

datetime <- gsub(" ", "_", Sys.time())
datetime <- gsub(":", "-", datetime)


url_epa01_iwsys <-
  "https://data.epa.gov/efservice/WATER_SYSTEM/EPA_REGION/01/PWS_ACTIVITY_CODE/I/CSV"

iwater_system_fresh <- read_csv(url_epa01_iwsys, col_types = cols(.default = "c"))


ipac_vals <- sort(unique(iwater_system_fresh$WATER_SYSTEM.PRIMACY_AGENCY_CODE))

url_base_iviol <- "https://data.epa.gov/efservice/VIOLATION/PWS_ACTIVITY_CODE/I/PRIMACY_AGENCY_CODE/"

iviolation_fresh <- list()

for (i in 1:length(ipac_vals)) {
  viols <- read_csv(paste0(url_base_iviol, ipac_vals[i], "/CSV"),
                    col_types = cols(.default = "c"))
  iviolation_fresh[[i]] <- viols
  
}


iviolation_fresh <- do.call(bind_rows, iviolation_fresh)


iviolation_fresh %>% 
  group_by(VIOLATION.PRIMACY_AGENCY_CODE) %>% 
  tally()


# iviolation_fresh %>% 
#   write_csv(paste0("C:/Users/Jim/OneDrive/CFB/R_exports/SDWIS_tracking/iviolation_", 
#                    datetime, ".csv"))
# iwater_system_fresh %>% 
#   write_csv(paste0("C:/Users/Jim/OneDrive/CFB/R_exports/SDWIS_tracking/iwater_system_", datetime, ".csv"))


```



```{r}

iviolation_fresh <- iviolation_fresh %>% 
  mutate(VIOLATION.COMPL_PER_BEGIN_DATE = dmy(VIOLATION.COMPL_PER_BEGIN_DATE)) %>% 
  filter(TRUE)

summary(iviolation_fresh$VIOLATION.COMPL_PER_BEGIN_DATE)

```


#### From Mika 2017

**try for interactions, univariate testing, etc.**

```{r}
library(modelr)
set.seed(1) 
folds <- crossv_kfold(sleep_data, k = 5)
folds
```


```{r}
library(dplyr)
library(purrr)
folds <- folds %>% mutate(model = map(train, ~ lm(dur ~ ., data = .)))
folds
```

```{r}
folds %>% mutate(predicted = map2(model, test, ~ augment(.x, newdata = .y)))
```

```{r}
library(tidyr)
cv.pred <- folds %>% mutate(predicted = map2(model, test, ~ augment(.x, newdata = .y))) %>% unnest(predicted)
head(cv.pred)
```

#### This, paste "*"

```{r}
vars <- colnames(select(sleep_data,-dur))
allsubmodels <- combn(vars,6)
Formulas <- apply(allsubmodels,2, function(x) paste("dur ~",paste(x,collapse="+")))
head(Formulas)
```


```{r}
library(broom)
library(dplyr)
library(tidyr)
set.seed(1)
folds <- crossv_kfold(sleep_data, k = 6) # start over

Model_validation <- list()

for(i in seq_along(Formulas)){
  SSE <- folds %>% 
    mutate(model = map(train, ~ lm(as.formula(Formulas[i]), data = .))) %>%
    unnest(predicted = map2(model, test, ~ augment(.x, newdata = .y))) %>%
    summarize(SSE =  sum(dur - .fitted)^2)
  Model_validation[[i]] <- tibble(formula = Formulas[i], SSE = as_vector(SSE))
}

bind_rows(Model_validation) %>% arrange(SSE) %>% head()
```




